---
title: "ASSIN_2_NEC"
author: "Nyein Ei Cho"
date: "10/25/2021"
output: html_document
---
1. Reformat this data frame to obtain the weight as a double numeric into one column

```{r}
weight<-c(104,96,95,91,87,81,77,75,112,118)
typeof(weight)
mode(weight)
```

2. the time of measurement as factor with two levels before_diet and after_diet

```{r}
time<-c("before_diet","after_diet")

time.fact<-as.factor(time)
time.fact
levels(time.fact)
```

3.Store this data frame as the first element of a list called BUBBLE_DIET.

```{r}
BUBBLE_DIET<- data.frame(time.fact, weight)
BUBBLE_DIET

str(BUBBLE_DIET)
```



4. a numeric vector (double) indicating the weight loss (in %) of each subject
```{r}
percent<-c(7.692308,4.210526,6.896552,2.597403,-5.357143)
library(scales)
wt_loss<-c(0.07692308,0.04210526,0.06896552,0.02597403,-0.05357143)
wt_lossinper<-percent(wt_loss)
wt_lossinper
```

5. a vector of character extracting the row names of the table previously created;
```{r}
subject<-c("subject_1","subject_2","subject_3","subject_4","subject_5")
typeof(subject)
```

6. combine these two elements in a table with two columns: subject and weight_loss. 
```{r}

weight_loss<-percent(wt_loss)
WEIGHT_LOSS<- data.frame(subject, weight_loss)
WEIGHT_LOSS
```

7. a list called BUBBLE_DIET
```{r}
BUBBLE_DIET.lst <- list(BUBBLE_DIET= BUBBLE_DIET, WEIGHT_LOSS = WEIGHT_LOSS)
BUBBLE_DIET.lst

WEIGHT_LOSS.lst <- list(subject= subject,weight_loss=weight_loss, WEIGHT_LOSS = WEIGHT_LOSS)
WEIGHT_LOSS.lst

BUBBLE_DIET.lst <- list(BUBBLE_DIET= BUBBLE_DIET, WEIGHT_LOSS.lst = WEIGHT_LOSS.lst)
BUBBLE_DIET.lst
```
```{r}

```

